State of the Practice for Medical Imaging Software

### 2022-04-20 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Fixed some typos

\begingroup
\renewcommand{\arraystretch}{0.85}
\begin{table}[!ht]
\centering
\begin{tabular}{llllll}
\toprule
Software & Comm.\ rank & Our rank & Stars/yr & Watches/yr & Forks/yr \\ 
\midrule
3D Slicer & 1 & 1 & 284 & 19 & 128 \\
OHIF Viewer & 2 & 3 & 277 & 19 & 224 \\
dwv & 3 & 23 & 124 & 12 & 51 \\
ImageJ & 4 & 2 & 84 & 9 & 30 \\
ParaView & 5 & 5 & 67 & 7 & 28 \\
Horos & 6 & 12 & 49 & 9 & 18 \\
Papaya & 7 & 17 & 45 & 5 & 20 \\
Fiji & 8 & 4 & 44 & 5 & 21 \\
DICOM Viewer & 9 & 29 & 43 & 6 & 9 \\
INVESALIUS 3 & 10 & 10 & 40 & 4 & 17 \\
Weasis & 11 & 6 & 36 & 5 & 19 \\
dicompyler & 12 & 26 & 35 & 5 & 14 \\
OsiriX Lite & 13 & 9 & 34 & 9 & 24 \\
MRIcroGL & 14 & 18 & 24 & 3 & 3 \\
GATE & 15 & 25 & 19 & 6 & 26 \\
Ginkgo CADx & 16 & 14 & 19 & 4 & 6 \\
BioImage Suite Web & 17 & 8 & 18 & 5 & 7 \\
Drishti & 18 & 27 & 16 & 4 & 4 \\
Slice:Drop & 19 & 20 & 10 & 2 & 5 \\
ITK-SNAP & 20 & 15 & 9 & 1 & 4 \\
medInria & 21 & 7 & 7 & 3 & 6 \\
SMILI & 22 & 13 & 3 & 1 & 2 \\
MatrixUser & 23 & 28 & 2 & 0 & 0 \\
MicroView & 24 & 16 & 1 & 1 & 1 \\
Gwyddion & 25 & 11 & n/a & n/a & n/a \\
XMedCon & 26 & 19 & n/a & n/a & n/a \\
DicomBrower & 27 & 21 & n/a & n/a & n/a \\
AMIDE & 28 & 22 & n/a & n/a & n/a \\
3DimViewer & 29 & 24 & n/a & n/a & n/a \\ 
\bottomrule
\end{tabular}
\caption{Software ranking by our methodology versus the community (Comm.)
ranking using GitHub metrics (Sorted in descending order of community
popularity, as estimated by the number of new stars per year)}
\label{tab_ranking_vs_GitHub}
\end{table}
\endgroup

@@

Table~\ref{tab_user_support_model} summarizes the user support models by the
number of projects using each model (projects may use more than one support
model). We do not know whether the prevalent use of GitHub issues for user
support is by design, or whether this just naturally happenes as users seek
help. The common use of GitHub by MI developers is not surprising, given that
GitHub is the largest code host in the world, with over 128 million public
repositories and over 23 million users (as of roughly February 26, 2020)
\citep{Kashyap2020}.

>>>>

\begingroup
\renewcommand{\arraystretch}{0.85}
\begin{table}[!ht]
\centering
\begin{tabular}{llllll}
\toprule
Software & Comm.\ rank & Our rank & Stars/yr & Watches/yr & Forks/yr \\ 
\midrule
3D Slicer & 1 & 1 & 284 & 19 & 128 \\
OHIF Viewer & 2 & 3 & 277 & 19 & 224 \\
dwv & 3 & 23 & 124 & 12 & 51 \\
ImageJ & 4 & 2 & 84 & 9 & 30 \\
ParaView & 5 & 5 & 67 & 7 & 28 \\
Horos & 6 & 12 & 49 & 9 & 18 \\
Papaya & 7 & 17 & 45 & 5 & 20 \\
Fiji & 8 & 4 & 44 & 5 & 21 \\
DICOM Viewer & 9 & 29 & 43 & 6 & 9 \\
INVESALIUS 3 & 10 & 10 & 40 & 4 & 17 \\
Weasis & 11 & 6 & 36 & 5 & 19 \\
dicompyler & 12 & 26 & 35 & 5 & 14 \\
OsiriX Lite & 13 & 9 & 34 & 9 & 24 \\
MRIcroGL & 14 & 18 & 24 & 3 & 3 \\
GATE & 15 & 25 & 19 & 6 & 26 \\
Ginkgo CADx & 16 & 14 & 19 & 4 & 6 \\
BioImage Suite Web & 17 & 8 & 18 & 5 & 7 \\
Drishti & 18 & 27 & 16 & 4 & 4 \\
Slice:Drop & 19 & 20 & 10 & 2 & 5 \\
ITK-SNAP & 20 & 15 & 9 & 1 & 4 \\
medInria & 21 & 7 & 7 & 3 & 6 \\
SMILI & 22 & 13 & 3 & 1 & 2 \\
MatrixUser & 23 & 28 & 2 & 0 & 0 \\
MicroView & 24 & 16 & 1 & 1 & 1 \\
Gwyddion & 25 & 11 & n/a & n/a & n/a \\
XMedCon & 26 & 19 & n/a & n/a & n/a \\
DicomBrowser & 27 & 21 & n/a & n/a & n/a \\
AMIDE & 28 & 22 & n/a & n/a & n/a \\
3DimViewer & 29 & 24 & n/a & n/a & n/a \\ 
\bottomrule
\end{tabular}
\caption{Software ranking by our methodology versus the community (Comm.)
ranking using GitHub metrics (Sorted in descending order of community
popularity, as estimated by the number of new stars per year)}
\label{tab_ranking_vs_GitHub}
\end{table}
\endgroup

@@

Table~\ref{tab_user_support_model} summarizes the user support models by the
number of projects using each model (projects may use more than one support
model). We do not know whether the prevalent use of GitHub issues for user
support is by design, or whether this just naturally happens as users seek
help. The common use of GitHub by MI developers is not surprising, given that
GitHub is the largest code host in the world, with over 128 million public
repositories and over 23 million users (as of roughly February 26, 2020)
\citep{Kashyap2020}.
